\include{header.tex}
\begin{document}

%----------Personal Info-----------------
\textbf{\LARGE Chen Kaishang} \\
\vspace{5pt}
\begin{tabular}{l l}
    Address: &\quad Room 305, Takanawa 3-19-20,  \\
             &\quad Minato-ku, Tokyo, Japan, 108-0074\\
    Email:   &\quad kaishangchen@toki.waseda.jp\\
    Tel:     &\quad \Plus81\Minus80\Minus9660\Minus0803\\
    Date of birth: &\quad November 11, 1997, Shenzhen-China
\end{tabular}
\vspace{5pt}

%-----------Profile-----------------
\section{Profile}
\vspace{5pt}
Background in Software Engineering and AI\texttt{/}Machine Learning. Strong
intests in software, art\texttt{/}literature, psychology and AI's application
in these fields.  Recently developed interests in finance as an area for ML
application.  Enjoys both working alone on technical details and together with
people to exchange ideas.  Fluent in English, Japanese and Mandarin Chinese and
thrives in a fast-moving multicultural environment. 
    
\vspace{5pt}

%-----------EDUCATION-----------------
\section{Education}
\vspace{5pt}
\resumeSubHeadingListStart
    \resumeSubheading
      {Waseda University - Current}{Tokyo}
      {Master of Engineering in Computer Science and Engineering}{2021.09 - Expected 2023.09}
    \resumeSubheading
      {Waseda University - Graduated}{Tokyo}
      {Bachelor of Engineering in Computer Science and Engineering}{2017.09 - 2021.09}
    \resumeSubheading
      {University of Hong Kong - Dropped out}{Hong Kong}
      {Department of Engineering}{2016.09 - 2017.04}

\resumeSubHeadingListEnd
\vspace{5pt}

%-----------Work Experience-----------------
\section{Work Experience}
\vspace{5pt}
\resumeSubHeadingListStart
    \resumeSubheading{Celsys, Inc.}{Tokyo}
    {Technical Intern}{2020.06 - 2021.11}
    \resumeItemListStart
        \resumeItem{Deep Learning}{Developed a semi-supervised deep learning model for detecting Japanese text in Comic images using Pytorch and Python}
        \resumeItem{Backend Web Server}{Wrapped the deep learning model into a web server using Docker and Django}
        \resumeItem{Desktop Application}{Developed a desktop GUI application for MacOS with proprietary C\Plus\Pluss libraries in XCode}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{5pt}

%-----------Papers-----------------
\section{Conference Appearance}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubheading{Multi-Agent Competition for Pokemon AI}{Accepted oral at Visual Computing 2021}
{Chen Kaishang, Kotaro Kikuchi, Edgar Simo-Serra}{}
\resumeSubHeadingListEnd
\vspace{5pt}

%-----------Project-----------------
\section{Projects}
\vspace{5pt}
\begin{itemize}[leftmargin=*]
    \item{\textbf{Research - Reinforcement Learning with Evolution Strategies on Imperfect Information Games}}
        \begin{itemize}
                \vspace{-5pt}
                \item Addresses poor learning stability and data efficiency in Reinforcement Learning.
                \item Implemented custom learning environment for the game Pokemon using the OpenAI Gym interface. 
                \item Achieved better learning stability by applying Evolution Strategies on existing reinforcement learning algorithms.
        \end{itemize}
    \vspace{-10pt}
    \item{\textbf{Intern - Semi-supervised text detection in non-photorealistic images}}
        \begin{itemize}
                \vspace{-5pt}
                \item Managed to train a CNN-based neural network on text detection task with predominantly synthetic data.
                \item Implemented a web server with Django to make the model accessible to http requests.
                \item Created a frontend GUI to interact with the web server using proprietary C\Plus\Pluss libraries.
        \end{itemize}
    \vspace{-10pt}
    \item{\textbf{Course Projects}}
        \begin{itemize}
                \vspace{-5pt}
                \item Computer Vision\texttt{/}Graphics: Natural image generation with generative adversarial networks(GANs).
                \item Language Processing: Semantics classification and Text Summarization on small corpuses.
                \item Learning on Various video games such as snake, pacman, tetris, etc.
        \end{itemize}
\end{itemize}
\vspace{5pt}

%-----------Skills-----------------
\section{Skills}
\vspace{5pt}
\begin{itemize}[leftmargin=*]
	\resumeSubItem{Machine Learning}{Pytorch, Tensorflow, Scikit-Learn, OpenAI Gym, etc.}
	\resumeSubItem{Data Analysis and Visualization}{Jupyter Notebook, Pandas, matplotlib\texttt{/}seaborn, Microsoft Excel, etc.}
	\resumeSubItem{Web Backend}{node.js, Django}
	\resumeSubItem{Automation}{Experience in creating automation scripts in Python and shell scripts.}
    \resumeSubItem{Platforms}{Linux (Desktop\&Server), Google Cloud Platform.}
	\resumeSubItem{Programming Languages}{Python, R, C\Plus\Plus, Go, bash, NodeJS\texttt{/}TypeScript, Java, C, Ocaml.}
    \resumeSubItem{Communication skills}{Fluent in English, Japanese and Madarin. Experiences in academic writing in English.}
\end{itemize}

\end{document}

